\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-24 4-3-water-level.Rmd
fix figure 7

River level and rainfall data for the same areas should have some similarity. Here we examine the river gauge data (\code{Water_course_level}) from the Bureau of Meteorology [@bom] in relation to weather station rainfall from NOAA's climate data [@noaa] (\code{climate}). Figure \ref{fig:matching-map} shows the location of available weather stations and water gauges in Victoria. The goal is to match water gauges with nearby weather stations, spatially and temporally, using 2020 measurements using 
\code{match_sites()} function.
<!--The Bureau of Meteorology collects [water data](http://www.bom.gov.au/metadata/catalogue/19115/ANZCW0503900528?template=full) from river gauges. The collected variables include: electrical conductivity, turbidity, watercourse discharge, watercourse level, and water temperature. We expect that the water level should be related to the precipitation available from climate data, since rainfall will raise the water level in the river. Figure \ref{fig:matching-map} shows the location of available weather stations and water gauges in Victoria, and we will try to match water gauges with nearby weather stations, taking into account both spatial and temporal information from 2020.-->

@@

```{r matching-map, fig.height = 7, fig.width=10, fig.cap="Location of weather stations and river gauges in Victoria, Australia."}
vic_map <- rmapshaper::ms_simplify(ozmaps::abs_ste %>%
               filter(NAME == "Victoria"))

ggplot() + 
  geom_sf(data = vic_map, fill = "grey95", color = "white") + 
  geom_point(data = dplyr::bind_rows(river, climate), 
             aes(x = long, y = lat, color = type)) + 
  ggthemes::theme_map() +
  theme(legend.position = "bottom") +
  labs(x = "Longitude", y = "Latitude") + 
  scale_color_brewer(palette = "Dark2") 
```

@@

```{r echo = TRUE}
res <- match_sites(
  river, climate,
  temporal_by = c("Water_course_level" = "prcp"),
  temporal_independent = "prcp",  
  temporal_n_highest = 30,
  temporal_min_match = 15
)
```

@@

Figure \ref{fig:matching} shows four matched pairs on the map (A) and standardised data as time series (B). The expected concurrent increase in precipitation and water level can be seen clearly.

```{r matching, out.width="100%", fig.height = 5, fig.width = 10, fig.cap="Matched weather stations and river gauges on the map (A) and across time (B). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here."}
p1 <-ggplot() + 
  geom_sf(data = vic_map, fill = "grey95", color = "white") + 
  geom_point(data = res, aes(x = long, y = lat, color = type)) +
  ggrepel::geom_label_repel(
    data = res %>% filter(type == "river"), aes(x = long, y = lat, label = group)) +
  scale_color_brewer(palette = "Dark2")  + 
  ggthemes::theme_map() +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::labs(x = "Longitude", y = "Latitude")

@@

(p1 | p2) + 
  patchwork::plot_layout(guides = "collect") + 
  plot_annotation(tag_levels = 'A')&
  theme(legend.position = "bottom")
```

>>>>

River level and rainfall data for the same areas should have some similarity. Here we examine the river gauge data (\code{Water_course_level}) from the Bureau of Meteorology [@bom] in relation to weather station rainfall from NOAA's climate data [@noaa] (\code{climate}). The goal is to match water gauges with nearby weather stations, spatially and temporally, using 2020 measurements using \code{match_sites()} function.
<!--The Bureau of Meteorology collects [water data](http://www.bom.gov.au/metadata/catalogue/19115/ANZCW0503900528?template=full) from river gauges. The collected variables include: electrical conductivity, turbidity, watercourse discharge, watercourse level, and water temperature. We expect that the water level should be related to the precipitation available from climate data, since rainfall will raise the water level in the river. Figure \ref{fig:matching-map} shows the location of available weather stations and water gauges in Victoria, and we will try to match water gauges with nearby weather stations, taking into account both spatial and temporal information from 2020.-->

@@

@@

```{r echo = TRUE}
res <- match_sites(
  river, climate,
  temporal_by = c("Water_course_level" = "prcp"),
  temporal_independent = "prcp",  
  temporal_n_highest = 30,
  temporal_min_match = 15, 
)
```

@@

Figure \ref{fig:matching} shows four matched pairs on the map (a) and standardised data as time series (b). The expected concurrent increase in precipitation and water level can be seen clearly.

```{r matching, out.width="100%", fig.height = 5, fig.width = 10, fig.cap="Weather stations and river gauges with matched pairs labelled on the map (a) and plotted across time (b). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here."}
vic_map <- ozmaps::abs_ste %>% 
  filter(NAME == "Victoria") %>% 
  rmapshaper::ms_simplify()

p1 <-ggplot() + 
  geom_sf(data = vic_map, fill = "grey95", color = "white") + 
  geom_point(data = dplyr::bind_rows(river, climate), 
             aes(x = long, y = lat, color = type), alpha = 0.2, fill = 0.2) +
  geom_point(data = res, aes(x = long, y = lat, color = type)) +
  ggrepel::geom_label_repel(
    data = res %>% filter(type == "river"), aes(x = long, y = lat, label = group)) +
  scale_color_brewer(palette = "Dark2")  + 
  ggthemes::theme_map() +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::labs(x = "Longitude", y = "Latitude")

@@

(p1 | p2) + 
  patchwork::plot_layout(guides = "collect") + 
  plot_annotation(tag_levels = 'a')&
  theme(legend.position = "bottom")
```

### 2022-06-24 jss/cubble-jss.tex
fix figure 7

River level and rainfall data for the same areas should have some similarity. Here we examine the river gauge data (\code{Water_course_level}) from the Bureau of Meteorology \citep{bom} in relation to weather station rainfall from NOAA's climate data \citep{noaa} (\code{climate}). Figure \ref{fig:matching-map} shows the location of available weather stations and water gauges in Victoria. The goal is to match water gauges with nearby weather stations, spatially and temporally, using 2020 measurements using
\code{match_sites()} function.

{\centering \includegraphics{figures/matching-map-1}

\caption[Location of weather stations and river gauges in Victoria, Australia]{Location of weather stations and river gauges in Victoria, Australia.}\label{fig:matching-map}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> res <- match_sites(
+   river, climate,
+   temporal_by = c("Water_course_level" = "prcp"),
+   temporal_independent = "prcp",  
+   temporal_n_highest = 30,
+   temporal_min_match = 15
+ )
\end{CodeInput}
\end{CodeChunk}

@@

Figure \ref{fig:matching} shows four matched pairs on the map (A) and standardised data as time series (B). The expected concurrent increase in precipitation and water level can be seen clearly.

@@

\caption[Matched weather stations and river gauges on the map (A) and across time (B)]{Matched weather stations and river gauges on the map (A) and across time (B). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here.}\label{fig:matching}
\end{figure}
\end{CodeChunk}

>>>>

River level and rainfall data for the same areas should have some similarity. Here we examine the river gauge data (\code{Water_course_level}) from the Bureau of Meteorology \citep{bom} in relation to weather station rainfall from NOAA's climate data \citep{noaa} (\code{climate}). The goal is to match water gauges with nearby weather stations, spatially and temporally, using 2020 measurements using \code{match_sites()} function.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> res <- match_sites(
+   river, climate,
+   temporal_by = c("Water_course_level" = "prcp"),
+   temporal_independent = "prcp",  
+   temporal_n_highest = 30,
+   temporal_min_match = 15, 
+ )
\end{CodeInput}
\end{CodeChunk}

@@

Figure \ref{fig:matching} shows four matched pairs on the map (a) and standardised data as time series (b). The expected concurrent increase in precipitation and water level can be seen clearly.

@@

\caption[Weather stations and river gauges with matched pairs labelled on the map (a) and plotted across time (b)]{Weather stations and river gauges with matched pairs labelled on the map (a) and plotted across time (b). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The water level reflects the increase in precipitation. The numbers (1, 5, 6, 10) indicate the group index derived from spatial matching, only those that were selectd by temporal matching are shown here.}\label{fig:matching}
\end{figure}
\end{CodeChunk}
